---
title: "Data Augmentation for Imbalanced Regression - Illustration"
author: "Anonymous"
date: "31/10/2022"
output:
  pdf_document: 
    toc: yes
    number_sections: yes
  html_document:
    toc = yes
editor_options: 
  markdown: 
    wrap: sentence
---

*Import library*

```{=html}
<style>
body {
text-align: justify}
</style>
```

```{r library , include=FALSE}
library("ggplot2")
library("UBL")
library("MASS")
library("reticulate")
library("randomForest")
library("ks")
library("mclust")
library("kernelboot")
library("smotefamily")
library("synthpop")
library("mgcv")
library("Metrics")
library("earth")
library("mda")
library("pdp")
library("beepr")
library("statip")
library("seewave")

knitr::opts_chunk$set(echo = FALSE,warning=FALSE)

relance = F # = T to restart the simulations, F to work with the loaded workspace

# Workspace setting
setwd("C:/Users/user/OneDrive/Perso/Thèse/Travaux/Exogenous Sampling/Illustration")

if (relance == F){
  load("C:/Users/user/OneDrive/Perso/Thèse/Travaux/Exogenous Sampling/Illustration/WKS/wks-Illu-relance.RData")
}
```

# Dataset generation

## Population

We consider a bi-dimensional initial population $\mathcal{D}^p = (X^p,Y^p)$, of size $n^p = 10,000$ such as:\
$X \sim F_0 = \mathcal{B}\text{eta}(5,5)$ $Y \sim \mathcal{N}(\sin(7X -0.5)+10,0.1)$ where ${\cal B}$ denotes the Beta distribution and ${\cal N}$ denotes the Gaussian distribution.

```{r genPop}
if (relance == T){
  n_pop = 10000 # size of the population
  alpha_pop = 5 # parameter of X distribution in the population
  beta_pop = 5 # parameter of X distribution in the population
  X_pop = rbeta (n_pop,alpha_pop, beta_pop)
  hist(X_pop,breaks = 100)
  pop = data.frame(X=X_pop)
}
```

Generation of $Y$ as a function of $X$ according to the non-linear relationship :

```{r genPop2}
if (relance == T){
  for (i in (1:nrow(pop))){
    pop$Y[i] = rnorm(1,sin(pop$X[i]*7 - 0.5) +10 ,0.1)
  }
}
plot(pop$X,pop$Y)
```

## Sampling

The test, balanced, and imbalanced samples are all of size $n=1,000$.

### Test sample

From this population, we uniformly draw a test sample $\mathcal{D}^t$.

```{r echantillonnage}
if (relance == T){
  base=pop
  n_ech = 1000
  ind_test = sample(nrow(base),n_ech)
  test = base[ind_test,]
  base = base[-ind_test,]
  y_test = test$Y
  test$Y = NULL
}
```

### Balanced sample

From the remaining population, $\mathcal{D}^p$ \\ $\mathcal{D}^t$, we uniformly draw a balanced sample $\mathcal{D}^b$, supposed to be representative of the population.

```{r}
if (relance == T){
  ech_rep = base[sample(nrow(base),n_ech),]
}
```

### Imbalanced sample

Finally, we draw an imbalanced sample $\mathcal{D}^i$ from this remaining population. The draw weights to construct this imbalanced sample are defined by the distribution $F = \mathcal{B}\text{eta}(9,9)$.

```{r}
plot(dbeta(x=seq(0,1,0.01), alpha_pop, beta_pop), col="green3", type = 'l')
lines(dbeta(x=seq(0,1,0.01),9 ,9 ), col="darkred")
```

```{r genEch}
if (relance == T){
  ech = base[sample(nrow(base),n_ech,prob = dbeta(base$X,9,9)),]
  X_ech = ech$X
  ech0 = ech
}

```

Graphical analysis

```{r genEchGraph}

df_train=data.frame(ech$X,rep("imb",length(ech$X)))
df_test=data.frame(pop$X,rep("pop",length(test$X)))
colnames(df_train)=c("X","dataset")
colnames(df_test)=c("X","dataset")
df = rbind(df_train,df_test)

ggplot(df, aes(X, color=dataset, fill=dataset)) + 
  geom_histogram(alpha = 0.5,aes(y = ..density..),bins=100,position="identity", legend="none")+
  geom_density(alpha=0.5)+
  scale_color_manual(values = c("pop" = "azure4", "imb" = "darkred")) + 
  scale_fill_manual(values = c("pop" = "azure4", "imb" = "darkred")) +
  theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
ggsave("Sorties/comp_X_Ech0-vs-Pop-Dens.png",width=7.29, height=4.5)

ggplot(df, aes(X, color=dataset, fill=dataset)) + 
  geom_histogram(alpha = 0.5,aes(y = ..density..),bins=100,position="identity", legend="none")+
  scale_color_manual(values = c("pop" = "azure4", "imb" = "darkred")) + 
  scale_fill_manual(values = c("pop" = "azure4", "imb" = "darkred")) +
  theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
ggsave("Sorties/comp_X_Ech0-vs-Pop.png",width=7.29, height=4.5)

ggplot() + 
  geom_point(aes(x=pop$X, y=pop$Y, colour="pop")) + 
  geom_point(aes(x=ech0$X, y=ech0$Y, colour="imb"))+
  scale_color_manual(name = "dataset",values = c("pop" = "azure4", "imb" = "darkred")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) +
  xlab("X") + ylab("Y")
ggsave("Sorties/comp_Y_Ech0-vs-Pop.png",width=7.29, height=4.5)


df_train=data.frame(ech$X,rep("imb",length(ech$X)))
df_test=data.frame(test$X,rep("test",length(test$X)))
colnames(df_train)=c("X","dataset")
colnames(df_test)=c("X","dataset")
df = rbind(df_train,df_test)

ggplot(df, aes(X, color=dataset, fill=dataset)) + 
  geom_histogram(alpha = 0.5,aes(y = ..density..),bins=100,position="identity")+
  scale_color_manual(values = c("darkred","darkgreen")) + 
  scale_fill_manual(values = c("darkred","darkgreen")) +
  theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))

```

Imbalanced analysis for the definition of Imbalanced Covariates Regression.

```{r illuUR}
# threshold 
a = 0.3
b = 0.7

# alpha 
(1-pbeta(b,5,5))/(1-pbeta(b,9,9)) - 1

# beta
pbeta(a,5,5)
1-pbeta(b,5,5)

```

we face an imbalanced regression: a $(\alpha, \beta)$-imbalanced problem with, for example, $\lvert \frac{\widehat{\mathbb{P}}(\boldsymbol{X}\in\chi)}{\mathbb{P}_0(\boldsymbol{X}\in\chi)} - 1 \rvert > \alpha$ when $\chi:= [0,0.3]$ or $\chi:= [0.7,1]$ and ($\alpha \leq 0.59, \beta \leq 0.09$). Here we are in the situation where $F$ and $F_0$ have the same support and the imbalanced problem will be less with $n$ large.

### Impact of imbalanced : Test dataset prediction

#### Generalized Additive Model

```{r predGAM_pop_v0, echo=FALSE, include=TRUE}
dat = ech_rep

# Predictions
reg = gam(Y ~  s(X) , data = dat)
y_pred = predict(reg,test)
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
devExp = res$dev.expl ; print(paste0("deviance expliquee : " , round(devExp*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_line(aes(y=y_pred), lwd=1.5, col="darkred")
```

```{r predGAM_ech0_v0, echo=FALSE, include=TRUE}
dat = ech0

# Predictions
reg = gam(Y ~  s(X) , data = dat)
p = predict(reg,test,type = "link", se.fit = TRUE)
y_pred = p$fit

res = summary(reg)
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicateors
devExp = res$dev.expl ; print(paste0("deviance expliquee : " , round(devExp*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_line(aes(y=y_pred), lwd=1.5, col="darkred")

```

#### Random Forest

```{r predRF_pop_v0, echo=FALSE, include=TRUE}
dat = ech_rep

# Predictions
reg = randomForest( Y ~ ., data = dat)
y_pred = predict(reg,test)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
rsq = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(rsq*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_point(aes(y=y_pred), col="darkred", lwd=0.9) + stat_smooth(aes(y=y_pred), lwd=1.5, col="darkred", method='loess')
```

```{r predRF_ech0_v0, echo=FALSE, include=TRUE}
dat = ech0

# Predictions
reg = randomForest( Y ~ ., data = dat)
y_pred = predict(reg,test)
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
rsq = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(rsq*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_point(aes(y=y_pred), col="darkred", lwd=0.9) + stat_smooth(aes(y=y_pred), lwd=1.5, col="darkred", method='loess')
```

#### Multivariate Adaptative Spline Regression

```{r predMARS_pop, echo=FALSE, include=TRUE}
dat = ech_rep

# Predictions
reg = earth( Y ~ ., data = dat)
y_pred = predict(reg,test)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
rsq = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(rsq*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_line(aes(y=y_pred), lwd=1.5, col="darkred")
```

```{r predMARS_ech0, echo=FALSE, include=TRUE}
dat = ech0

# Predictions
reg = earth( Y ~ ., data = dat)
y_pred = predict(reg,test)
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
rsq = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(rsq*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_line(aes(y=y_pred), lwd=1.5, col="darkred")
```

```{r predMARS2_pop_v0, echo=FALSE, include=TRUE}
dat = ech_rep

# Predictions
reg = mars(dat$X ,dat$Y)
y_pred = predict(reg,test)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
rsq = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(rsq*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_line(aes(y=y_pred), lwd=1.5, col="darkred")
```

```{r predMARS2_ech0_v0, echo=FALSE, include=TRUE}
dat = ech0

# Predictions
reg = mars(dat$X ,dat$Y)
y_pred = predict(reg,test)
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

# Indicators
rsq = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(rsq*100,2)))
rmse = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(rmse,2)))
R2 = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(R2*100,2)))

# Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  geom_line(aes(y=y_pred), lwd=1.5, col="darkred")
```

# Sample Adjustement

To handle the imbalance, we want to draw a $n^*$-sample, $\{(\boldsymbol{X}^*_i,Y^*_i)_{i=1,\cdots,n^*}\}$ from the initial $n$-sample $\{(\boldsymbol{X}_i,Y_i)_{i=1,\cdots,n}\}$, such that the cdf $F^*$ of $\boldsymbol{X^*}$ converges to the target $F_0$ with associated probability $\mathbb{P}_0$.

We wish to redress the initial distribution of $X$ (in black) as follows (in red):

```{r histInit_cible}
ggplot(ech, aes(X)) + 
  geom_histogram(alpha = 0.5, aes(y = ..density..,color= "imb"),position = 'identity',bins=100, fill="darkred")+
  geom_density(alpha=0.5, fill = "darkred")+
  geom_line(aes(y=dbeta(ech$X,alpha_pop,beta_pop),colour="f0"), lwd=2,linetype = 1)+
  scale_color_manual(name = "dataset",values = c("f0" = "darkgreen", "imb" = "darkred")) +
  theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))

ggsave("Sorties/Hist_X_Ech0-vs-Tgt.png",width=7.29, height=4.5)

```

## Weighted Resampling (WR) algorithm

Resampling weights definition

```{r WB}
# Target dstribution : population
Pt = function(x){
  dbeta(x,alpha_pop,beta_pop)
}

X = ech$X
pe = density(X,n=length(X)) # emmpiric distribution  : kernel estimator
ech$pe = approx(pe$x,pe$y,xout=ech$X)$y
ech$pt = Pt(X)
ech$w = ech$pt / ech$pe
ech$q = ech$w / sum(ech$w)

ggplot(ech, aes(x=X)) + geom_point(aes(y=q), colour="darkred") + labs(y = "weight")
ggsave("Sorties/weights-ech0.png",width=7.29, height=4.5)

```

Drawing

```{r Drawing}
if (relance == T){
  # Drawing
  ech_add = sample(seq(1, nrow(ech)),n_ech,replace=T,prob = ech$q)
  ech_add = ech[ech_add,]
  
  # Variable selection
  filtre_var = c("X","Y")
  ech_add = ech_add[,filtre_var]
  ech0 = ech0[,filtre_var]
}
```

Obtained distribution after resampling

```{r histWB_cible}
ggplot(ech_add, aes(X)) + 
  geom_histogram(alpha = 0.5, aes(y = ..density..,color= "WR"),position = 'identity',bins=100, fill="darkred")+
  geom_density(alpha=0.5, fill = "darkred")+
  geom_line(aes(y=dbeta(ech_add$X,alpha_pop,beta_pop),colour="f0"), lwd=2,linetype = 1)+
  scale_color_manual(name = "dataset",values = c("f0" = "darkgreen", "WR" = "darkred")) +
  theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))

ggsave("Sorties/Hist_X_Ech_add-vs-Tgt.png",width=7.29, height=4.5)

```

This last figure shows the new sample $\mathcal{D}^*$ which is closer to target distribution than the initial one. However, the values on the sides, quite rare, are naturally very drawn. We see there are still some parts of the support without observation, especially on the right side. This situation could lead to an overfitting phenomenon because the same observations are replicated several times and could lead to an over-fitting effect. To improve the weighted resampling, we propose to combine it with a synthetic data generation.

## Data Augmentation - Weighted Resampling algorithm

### Generation by random noise

#### Gaussian Noise (GN)

**Gaussian Noise on the augmented dataset and application of WR algorithm**

```{r GN, echo=FALSE}
if (relance == T){
  ### Approche GN (cf fonction Gn.exsClassif : https://rdrr.io/github/paobranco/UBL/src/R/gaussNoiseClassif.R
  N = 100000
  pert = 0.3 
  
  for (tir in seq(round(N/nrow(ech_add)))){
    ech_GN=ech_add
    for (j in (1:ncol(ech_add))) {
      ech_GN[, j] = ech_add[, j] + rnorm(nrow(ech_add), 0, sd(ech0[,colnames(ech0)[j]]) * pert)
    }
    if (tir==1){
      ech_GN_SC = ech_GN
    }else{
      ech_GN_SC = rbind(ech_GN_SC,ech_GN)
    }
  }
  
  # Drawing weights
  X = ech_GN_SC$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_GN_SC$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_GN_SC)),n_ech,replace=T,prob = q)
  ech_GN_SC = ech_GN_SC[ind,filtre_var]
}
```

Graphical analysis

```{r GN2, echo=FALSE}
ech_synth = ech_GN_SC
name_synth = "ech_GN_SC"

graph = function (ech_synth,name_synth){
  # Covariate analysis
  print(ggplot(ech_synth, aes(X)) + 
    geom_histogram(alpha = 0.5, aes(y = ..density..,color= "new"),position = 'identity',bins=100, fill="deepskyblue4")+
    geom_density(alpha=0.5, fill = "deepskyblue4")+
    geom_line(aes(y=dbeta(ech_synth$X,alpha_pop,beta_pop),colour="f0"), lwd=2,linetype = 1)+
    scale_color_manual(name = "dataset",values = c("f0" = "darkgreen", "new" = "deepskyblue4")) +
    theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")))
  ggsave(paste0("Sorties/Hist_X_",name_synth,"-vs-Tgt.png"),width=7.29, height=4.5)
  
  df_add=data.frame(ech_add$X,rep("WR",length(ech$X)))
  df_synth=data.frame(ech_synth$X,rep("new",length(ech_synth$X)))
  colnames(df_add)=c("X","dataset")
  colnames(df_synth)=c("X","dataset")
  df = rbind(df_add,df_synth)
  print(ggplot(df, aes(X, color=dataset, fill=dataset)) + 
    geom_histogram(alpha = 0.5, aes(y = ..density..),position = 'identity',bins=100)+
      #geom_density(alpha=0.5)+
    scale_color_manual(values=c("WR" = "darkred", "new" = "deepskyblue4"))+
    scale_fill_manual(values=c("WR" = "darkred", "new" = "deepskyblue4"))+
    theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")))
  ggsave(paste0("Sorties/Hist_X_",name_synth,"-vs-ech_add.png"),width=7.29, height=4.5)
  
  # Target variable analysis
  print(ggplot() + 
    geom_point(aes(x=ech_synth$X, y=ech_synth$Y, colour="new")) + 
    geom_point(aes(x=ech0$X, y=ech0$Y, colour="imb"))+
    scale_color_manual(name = "dataset",values = c("new" = "deepskyblue4", "imb" = "darkred")) + 
    theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))+
  xlab("X") + ylab("Y"))
  ggsave(paste0("Sorties/comp_Y_",name_synth,"-vs-ech0.png"),width=7.29, height=4.5)

}
graph(ech_synth,name_synth)

```

**Gaussian Noise on the augmented dataset, by cluster and application of WR algorithm**

```{r GN-GMM, include=FALSE}
if (relance == T){
  N = 100000
  DMC = densityMclust(ech0, plot=F,G=1:6)
  ech_MC = cbind(ech0,"cluster" = DMC$classification)
  cl = max(ech_MC$cluster)
  for (tir in seq(round(N/nrow(ech_add)))){
    for (i in (1:cl)){
        temp = ech_MC[ech_MC$cluster == i,]
        ech_add_temp = merge(temp, ech_add, on ="X")
        N = nrow(ech_add_temp)
        ech_GN=ech_add_temp
        for (j in (1:ncol(ech_add_temp))) {
          ech_GN[, j] = ech_add_temp[, j] +
            rnorm(nrow(ech_add_temp), 0, sd(temp[,colnames(temp)[j]]) * pert)
        }
        if (tir==1 & i==1){
          GN_GMM = ech_GN
        }else{
          GN_GMM = rbind(GN_GMM,ech_GN)
        }
    }
  }
  
  # Drawing weights
  X = GN_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=GN_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  
  # Drawing
  ind = sample(seq(1, nrow(GN_GMM)),n_ech,replace=T,prob = q)
  GN_GMM = GN_GMM[ind,filtre_var]
}
```

Graphical analysis

```{r cluster, echo=FALSE}
# Clustering analysis
ggplot(ech_MC, aes(x=X, y=Y, color=cluster)) + geom_point() + 
    theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
ggsave(paste0("Sorties/clustering.png"),width=7.29, height=4.5)
```

```{r GN-GMM2, echo=FALSE}
ech_synth = GN_GMM
name_synth = "GN_GMM"
graph(ech_synth,name_synth)

```

**Application of the Gaussian Noise for regression imbalanced, on the augmented dataset and application of WR algorithm**

```{r GN-classif, echo=FALSE}
if (relance == T){
  ech_GN_clust = GaussNoiseClassif(cluster ~ .,ech_MC, pert,C.perc = "balance")
}
hist(ech_GN_clust$X,breaks=100, col = "antiquewhite",freq=F,right = T)
points(ech_GN_clust$X,dbeta(ech_GN_clust$X,alpha_pop,beta_pop),col="red")
lines(density(ech_GN_clust$X),col="black",lwd=2)

hist(ech_GN_clust$X, col=rgb(0,0,1,1/4),breaks = 100,prob=T) 
hist(ech_add$X, col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T) 
hist(ech0$X,col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T)
plot(ech_GN_clust$X,ech_GN_clust$Y)
points(ech0$X,ech0$Y,col="red")
```

#### Multivariate kernel density estimator (ROSE & KDE)

*Estimator inspired by ROSE*

```{r ROSE, echo=FALSE}
if (relance == T){
  hmult=1
  n = nrow(ech0)
  q = ncol(ech0)
  n.new <- nrow(ech_add)
  cons.kernel <- (4/((q+2)*n))^(1/(q+4))
  if(q!=1){
    H <- hmult*cons.kernel*diag(apply(ech0, 2, sd), q)
  }else {
    H <- hmult*cons.kernel*sd(ech0)}
  Xnew.num <- matrix(rnorm(n.new*q), n.new, q)%*%H
  ech_ROSE_SC =data.frame(Xnew.num + ech_add)
  
  
  # Drawing weights
  X = ech_ROSE_SC$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_ROSE_SC$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_ROSE_SC)),n_ech,replace=T,prob = q)
  ech_ROSE_SC = ech_ROSE_SC[ind,filtre_var]
}
```

```{r ROSE_AnalyseY, echo=FALSE}
ech_synth = ech_ROSE_SC
name_synth = "ech_ROSE_SC"
graph(ech_synth,name_synth)
```

Application by cluster

```{r ROSE_GMM, echo=FALSE}
if (relance == T){
  ech_MC = cbind(ech0[,c("X","Y")],"cluster" = DMC$classification)
  ech_add_MC = merge(ech_MC, ech_add, on = filtre_var)
  cl = max(ech_MC$cluster)
  N = 100000
  
  for (tir in seq(round(N/nrow(ech_add)))){
    for (i in (1:cl)){
        temp = ech_MC[ech_MC$cluster == i,]
        temp_add = ech_add_MC[ech_add_MC$cluster == i,]
        n = nrow(temp)
        q = ncol(temp)
        n.new <- nrow(temp_add)
        cons.kernel <- (4/((q+2)*n))^(1/(q+4))
        if(q!=1){
          H <- hmult*cons.kernel*diag(apply(temp, 2, sd), q)
        }else {
          H <- hmult*cons.kernel*sd(temp)}
        Xnew.num <- matrix(rnorm(n.new*q), n.new, q)%*%H
        ech_ROSE =data.frame(Xnew.num + temp_add)
        if (tir == 1 & i == 1) {
        ROSE_GMM = ech_ROSE
      } else {ROSE_GMM = rbind(ROSE_GMM, ech_ROSE)}
    }
  }
  
  
  # Drawing weights
  X = ROSE_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ROSE_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ROSE_GMM)),n_ech,replace=T,prob = q)
  ROSE_GMM = ROSE_GMM[ind,filtre_var]
}

```

```{r ROSE_GMM_res, echo=FALSE}
ech_synth = ROSE_GMM
name_synth = "ROSE_GMM"
graph(ech_synth,name_synth)
```

*Smoothed Bootstrap (KDE)*

```{r smoothedbootstrap, echo=FALSE}
if (relance == T){
  # Drawing weights
  X = ech0$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech0$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  
  kde_boot = data.frame(rmvg(100000, ech0, weights =  q))
  
  # Drawing weights
  X = kde_boot$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=kde_boot$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(kde_boot)),n_ech,replace=T,prob = q)
  kde_boot = kde_boot[ind,filtre_var]
}

### Graphics
ech_synth = kde_boot
name_synth = "kde_boot"
graph(ech_synth,name_synth)
```

Application by cluster

```{r smoothedbootstrap2, echo=FALSE}
if (relance == T){
  # Drawing weights
  X = ech0$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech0$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  
  N = 100000
  ech_MC = cbind(ech0[,c("X","Y")],"cluster" = DMC$classification)
  ech_add_MC = merge(ech_MC, ech_add, on = filtre_var)
  cl = max(ech_MC$cluster)
  for (tir in seq(round(N/nrow(ech_add)))){
    for (i in (1:cl)){
      temp = data.frame(rmvg(sum(ech_add_MC$cluster == i), ech_MC[ech_MC$cluster == i,filtre_var], weights =  q[ech_MC$cluster==i]))
      if (tir == 1 & i ==1) {
      kde_boot_GMM = temp
    } else {kde_boot_GMM = rbind(kde_boot_GMM, temp)}
    }
  }
  
  
  # Drawing weights
  X = kde_boot_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=kde_boot_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(kde_boot_GMM)),n_ech,replace=T,prob = q)
  kde_boot_GMM = kde_boot_GMM[ind,filtre_var]
}

### Graphics
ech_synth = kde_boot_GMM
name_synth = "kde_boot_GMM"
graph(ech_synth,name_synth)
  
```

### Mixture model approach (latent structure model)

#### Gaussian Mixture Model (GMM)

```{r GMM1, include=FALSE}
if (relance == T){
  DMC = densityMclust(ech0, plot=F,G=1:6)
  ech_MC = cbind(ech0,"cluster" = DMC$classification)
}
```

```{r GMM2, echo=FALSE}
ggplot(ech_MC, aes(x=X, y=Y, color=cluster)) + geom_point()
```

```{r GMM_sim, include=FALSE}
if (relance == T){
  DS_GMM = as.data.frame(sim(modelName=DMC$modelName,parameters=DMC$parameters,n=100000))
  colnames(DS_GMM) = c("cluster",colnames(ech0))
  DS_GMM0 = DS_GMM
  # Drawing weights
  X = DS_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=DS_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(DS_GMM)),n_ech,replace=T,prob = q)
  GMM = DS_GMM[ind,filtre_var]
}
```

```{r GMM_sim2, echo=FALSE}
### Graphics
ech_synth = GMM
name_synth = "GMM"
graph(ech_synth,name_synth)
```

#### Factor analysis (FA)

```{r FA_simple, include=FALSE}
if (relance == T){
  ech = ech0
  
  if ("cluster" %in% colnames(ech)) {
    cl = max(ech$cluster)
    p = length(colnames(ech))-1
  }else {
    cl = 1
    p = length(colnames(ech))
  }
  phi = array(rep(0,cl*p),dim=c(1,p,cl))
  W = array(rep(0,cl*p*(p-1)),dim=c(p-1,p,cl))
  mu = array(rep(0,cl*p),dim=c(1,p,cl))
  for (i in (1:cl)){
    if ("cluster" %in% colnames(ech)) {
      temp = ech[ech$cluster == i,]
    } else {temp = ech}
    temp = temp[,c("X","Y")]
    p = length(colnames(temp))
    p_py = r_to_py(p,convert=TRUE)
    py_run_string("from sklearn.decomposition import FactorAnalysis")
    ech_py = r_to_py(temp,convert=TRUE)
    py_run_string("p=r.ech_py.shape[1]")
    py_run_string("transformer = FactorAnalysis(n_components=p-1, random_state=0)")
    py_run_string("X_transformed = transformer.fit_transform(r.ech_py)")
    py_run_string("noise_var = transformer.noise_variance_")
    py_run_string("mu = transformer.mean_")
    py_run_string("comp = transformer.components_")
    phi[,,i] = py$noise_var
    W[,,i] = py$comp
    mu[,,i] = py$mu
  }
  
  # Data generation
  for (i in (1:cl)){
    if ("cluster" %in% colnames(ech)) {
      n_ds = sum(ech$cluster == i)*10
    }else{n_ds = nrow(ech)*10}
    Z = mvrnorm(n_ds,rep(0,p-1),diag(rep(1,p-1)))
    temp = Z%*%W[,,i]  +  t(matrix(rep(mu[,,i],n_ds),p,n_ds)) + mvrnorm(n_ds,rep(0,p),diag(phi[,,i]))
    temp = as.data.frame(cbind(temp,cluster = i))
    if (i == 1) {
      DS_FA = temp
    }else {DS_FA = rbind(DS_FA,temp)}
  }
  DS_FA = as.data.frame(DS_FA)
  colnames(DS_FA) = c(colnames(ech0),"cluster")
  
  # Drawing weights
  X = DS_FA$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=DS_FA$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(DS_FA)),n_ech,replace=T,prob = q)
  DS_FA = DS_FA[ind,filtre_var]
}
```

```{r FA_simple_res, echo=FALSE}
plot(DS_FA$X,DS_FA$Y)
points(ech0$X,ech0$Y,col="red")
```

Application by cluster

```{r FA_cluster, include=FALSE}
if (relance == T){  
  DMC = densityMclust(ech0, plot=F,G=1:6)
  ech_MC = cbind(ech0,"cluster" = DMC$classification)
  
  ech = ech_MC
  
  if ("cluster" %in% colnames(ech)) {
    cl = max(ech$cluster)
    p = length(colnames(ech))-1
  }else {
    cl = 1
    p = length(colnames(ech))
  }
  phi = array(rep(0,cl*p),dim=c(1,p,cl))
  W = array(rep(0,cl*p*(p-1)),dim=c(p-1,p,cl))
  mu = array(rep(0,cl*p),dim=c(1,p,cl))
  for (i in (1:cl)){
    if ("cluster" %in% colnames(ech)) {
      temp = ech[ech$cluster == i,]
    } else {temp = ech}
    temp = temp[,c("X","Y")]
    p = length(colnames(temp))
    p_py = r_to_py(p,convert=TRUE)
    py_run_string("from sklearn.decomposition import FactorAnalysis")
    ech_py = r_to_py(temp,convert=TRUE)
    py_run_string("p=r.ech_py.shape[1]")
    py_run_string("transformer = FactorAnalysis(n_components=p-1, random_state=0)")
    py_run_string("X_transformed = transformer.fit_transform(r.ech_py)")
    py_run_string("noise_var = transformer.noise_variance_")
    py_run_string("mu = transformer.mean_")
    py_run_string("comp = transformer.components_")
    phi[,,i] = py$noise_var
    W[,,i] = py$comp
    mu[,,i] = py$mu
  }
  
  # Data generation
  for (i in (1:cl)){
    n_ds = sum(ech$cluster == i)*100
    Z = mvrnorm(n_ds,rep(0,p-1),diag(rep(1,p-1)))
    temp = Z%*%W[,,i]  +  t(matrix(rep(mu[,,i],n_ds),p,n_ds)) + mvrnorm(n_ds,rep(0,p),diag(phi[,,i]))
    temp = as.data.frame(cbind(temp,cluster = i))
    if (i == 1) {
      DS_FA = temp
    }else {DS_FA = rbind(DS_FA,temp)}
  }
  DS_FA_GMM = as.data.frame(DS_FA)
  colnames(DS_FA_GMM) = c(colnames(ech0),"cluster")
  
  # Drawing weights
  X = DS_FA_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=DS_FA_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(DS_FA_GMM)),n_ech,replace=T,prob = q)
  FA_GMM = DS_FA_GMM[ind,filtre_var]
}
```

```{r FA_cluster_res, echo=FALSE}
### Graphics
ech_synth = FA_GMM
name_synth = "FA_GMM"
graph(ech_synth,name_synth)
```

### Copula

```{r copula, include=FALSE}
if (relance == T){
  py_run_string("from sdv.tabular import GaussianCopula")
  ech_py = r_to_py(ech0,convert=TRUE)
  py_run_string("copule = GaussianCopula()")
  py_run_string("copule.fit(r.ech_py)")
  py_run_string("ech_copule_py = copule.sample(100000)")
  ech_copule = py$ech_copule_py
  
  # Drawing weights
  X = ech_copule$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_copule$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_copule)),n_ech,replace=T,prob = q)
  ech_copule = ech_copule[ind,filtre_var]
}
```

```{r copula_res, echo=FALSE}
### Graphics
ech_synth = ech_copule
name_synth = "ech_copule"
graph(ech_synth,name_synth)
```

### Conditional Generative Adversarial Net (GAN)

package CTGAN from SDV

*no conditional*

```{r GAN, echo=FALSE}
if (relance == T){
  py_run_string("from ctgan import CTGANSynthesizer")
  ech0_py = r_to_py(ech0,convert=TRUE)
  py_run_string("ctgan = CTGANSynthesizer(epochs=10000)")
  py_run_string("ctgan.fit(r.ech0_py)")
  py_run_string("ech_ctgan_py = ctgan.sample(100000)")
  ech_GAN = py$ech_ctgan_py
  
  # Drawing weights
  X = ech_GAN$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_GAN$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_GAN)),n_ech,replace=T,prob = q)
  ech_GAN = ech_GAN[ind,filtre_var]
}
```

```{r GAN_res, echo=FALSE}
### Graphics
ech_synth = ech_GAN
name_synth = "ech_GAN"
graph(ech_synth,name_synth)
```

On constate que la génération de $Y$ est très instable.

*application by cluster*

```{r GAN_cond, echo=FALSE}
if (relance == T){
  ech_MC = cbind(ech0[,c("X","Y")],"cluster" = DMC$classification)
  py_run_string("from ctgan import CTGANSynthesizer")
  ech_MC_py = r_to_py(ech_MC,convert=TRUE)
  py_run_string("discrete_columns = ['cluster']")
  py_run_string("ctgan = CTGANSynthesizer(epochs=10000)")
  py_run_string("ctgan.fit(r.ech_MC_py,discrete_columns)")
  py_run_string("ech_ctgan_py = ctgan.sample(50000)")
  ech_ctganSynth_GMM = py$ech_ctgan_py
  
  # Drawing weights
  X = ech_ctganSynth_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_ctganSynth_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_ctganSynth_GMM)),n_ech,replace=T,prob = q)
  ech_ctganSynth_GMM = ech_ctganSynth_GMM[ind,filtre_var]
}
```

```{r GAN_cond_res, echo=FALSE}
### Graphics
ech_synth = ech_ctganSynth_GMM
name_synth = "ech_GAN"
graph(ech_synth,name_synth)
```

### k-NN Interpolation

#### interpolation inspired by SMOTE (SMOTE)

```{r Smote, echo=FALSE}
if (relance == T){
  # Drawing weights
  X = ech0$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech0$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  
  ech = ech0
  
  k=3
  ech$id=seq(nrow(ech))
  
  n_pop = 10000 
  for (i in (1:n_pop)){
      id = sample(nrow(ech0),1,prob = q)
      knn_id = smotefamily::knearest(ech,ech[id,], n_clust=k)
      kppv = knn_id[sample(seq(k),1)]
      lambda = runif(1)
      new_obs = ech[id,] + lambda * (ech[kppv,]-ech[id,])
      rownames(new_obs)=i
      if (i==1){
        ech_smote = new_obs
      }else{
        ech_smote = rbind(ech_smote,new_obs)
      }
  }
  ech_smote$id = NULL
}
  
  # Drawing weights
  X = ech_smote$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_smote$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_smote)),n_ech,replace=T,prob = q)
  ech_smote = ech_smote[ind,filtre_var]


### Graphics
ech_synth = ech_smote
name_synth = "ech_smote"
graph(ech_synth,name_synth)
```

Application by cluster

```{r Smote_clust, echo=FALSE}
if (relance == T){
  # Drawing weights
  X = ech0$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech0$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  
  ech = ech0
  ech_MC = cbind(ech0,"cluster" = DMC$classification)
  cl = max(ech_MC$cluster)
  n_pop = 10000
  for (i in (1:n_pop)){
      id = sample(nrow(ech0),1,prob = q)
      temp = ech_MC[ech_MC$cluster == ech_MC$cluster[id],]
      knn_id = smotefamily::knearest(temp,ech_MC[id,], n_clust=k)
      kppv = knn_id[sample(seq(k),1)]
      lambda = runif(1)
      new_obs = ech_MC[id,] + lambda * (temp[kppv,]-ech_MC[id,])
      rownames(new_obs)=i
      if (i==1){
        ech_smote_GMM = new_obs
      }else{
        ech_smote_GMM = rbind(ech_smote_GMM,new_obs)
      }
  }
  ech_smote_GMM$id = NULL
  
  # Drawing weights
  X = ech_smote_GMM$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_smote_GMM$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_smote_GMM)),n_ech,replace=T,prob = q)
  ech_smote_GMM = ech_smote_GMM[ind,filtre_var]
}

### Graphics
ech_synth = ech_smote_GMM
name_synth = "ech_smote_GMM"
graph(ech_synth,name_synth)
```

SMOTE on the initial sample, binarised by clusters

```{r SmoteOrig_clust, echo=FALSE}
if (relance == T){
  ech_smote_clust = SmoteClassif(cluster ~ .,ech_MC)
}
hist(ech_smote_clust$X,breaks=100, col = "antiquewhite",freq=F,right = T)
points(ech_smote_clust$X,dbeta(ech_smote_clust$X,alpha_pop,beta_pop),col="red")
hist(ech_smote_clust$X, col=rgb(0,0,1,1/4),breaks = 100,prob=T) 
hist(ech_add$X, col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T) 
hist(ech0$X,col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T)
plot(ech_smote_clust$X,ech_smote_clust$Y)
points(ech0$X,ech0$Y,col="red")
```

#### Approches Utulity-Based Learning

1)  Error : "All the points have relevance 0. Please, redefine your relevance function!" 2 ) No possibility to define q as utility function : Error in GaussNoiseRegress(form = Y \~ ., dat = ech0, rel = rel) : All the points have relevance 1. Please, redefine your relevance function!
2)  too complicated to define q as a utility function (UBL an R package for ... : p.50)

Sur $Y$ :

```{r SmoGN_Y, echo=FALSE}
if (relance == T){
  try({
    ech_smoGN_Y = SMOGNRegress(Y ~ .,ech0)
    hist(ech_smoGN_Y$X,breaks=50, col = "antiquewhite",freq=F,right = T)
    points(ech_smoGN_Y$X,dbeta(ech_smoGN_Y$X,alpha_pop,beta_pop),col="red")
    hist(ech_smoGN_Y$X, col=rgb(0,0,1,1/4),breaks = 50,prob=T) 
    hist(ech_add$X, col=rgb(1,0,0,1/4),breaks = 50,prob=T, add=T) 
    hist(ech0$X,col=rgb(1,0,0,1/4),breaks = 50,prob=T, add=T)
    plot(ech_smoGN_Y$X,ech_smoGN_Y$Y)
    points(ech0$X,ech0$Y,col="red")
  })
}
```

Sur $X$ :

```{r SmoGN, echo=FALSE}
if (relance == T){
  ech_smoGN = SMOGNRegress(X ~ .,ech0)
} 
hist(ech_smoGN$X,breaks=50, col = "antiquewhite",freq=F,right = T)
points(ech_smoGN$X,dbeta(ech_smoGN$X,alpha_pop,beta_pop),col="red")
hist(ech_smoGN$X, col=rgb(0,0,1,1/4),breaks = 50,prob=T) 
hist(ech_add$X, col=rgb(1,0,0,1/4),breaks = 50,prob=T, add=T) 
hist(ech0$X,col=rgb(1,0,0,1/4),breaks = 50,prob=T, add=T)
plot(ech_smoGN$X,ech_smoGN$Y)
points(ech0$X,ech0$Y,col="red")
```

In both cases, this proposed solution does not meet the objective and the generation of DS is not interesting: low values of $Y$ in the first case and no orientation in the second.




### Random Forest (RF)

```{r}
if (relance == T){
  ech_RF=syn(ech0,method="rf", visit.sequence = c("X","Y"),k=1000, proper=T)
  ech_RF = ech_RF$syn
}
summary(ech_RF$X)
summary(ech0$X)
qqplot(ech_RF$X,ech0$X)

hist(ech_RF$X, col=rgb(0,0,1,1/4),breaks = 100,prob=T) 
hist(ech0$X, col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T) 

```

```{r Synthpop-RF, echo=FALSE}
if (relance == T){
  ech_RF = syn(ech0,method="rf", visit.sequence = c("X","Y"),k=10000)
  ech_RF = ech_RF$syn
}
hist(ech_RF$X,breaks=100, col = "antiquewhite",freq=F,right = T)
points(ech_RF$X,dbeta(ech_RF$X,alpha_pop,beta_pop),col="red")
hist(ech_RF$X, col=rgb(0,0,1,1/4),breaks = 100,prob=T)  
hist(ech_add$X, col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T) 
hist(ech0$X,col=rgb(1,0,0,1/4),breaks = 100,prob=T, add=T)
plot(ech_RF$X,ech_RF$Y)
points(ech0$X,ech0$Y,col="red")
```

Conditionnal application by cluster

```{r Synthpop-RF2, echo=FALSE}
if (relance == T){
  ech_RF2 = syn(ech_MC[,c("X","Y","cluster")],method="rf", visit.sequence = c("cluster","X","Y"),k=10000)
  ech_RF2 = ech_RF2$syn
  
  # Drawing weights
  X = ech_RF2$X
  pe = density(X,n=length(X))
  pe = approx(pe$x,pe$y,xout=ech_RF2$X)$y
  pt = Pt(X)
  w = pt / pe
  q = w / sum(w)
  # Drawing
  ind = sample(seq(1, nrow(ech_RF2)),n_ech,replace=T,prob = q)
  ech_RF2 = ech_RF2[ind,filtre_var]
}
```

```{r Synthpop-RF2_res, echo=FALSE}
### Graphics
ech_synth = ech_RF2
name_synth = "ech_RF"
graph(ech_synth,name_synth)
```

# Performance evaluation

## Generalized Additive Model Learning

```{r indic_GAM,echo=F}
gam_devExp = rep(0,16)
gam_rmse = rep(0,16)
gam_R2 = rep(0,16)
gam_hell_X = rep(0,16)
gam_hell_Y = rep(0,16)
gam_kl_X = rep(0,16)
gam_kl_Y = rep(0,16)
k=1
```

### Balanced sample

```{r predGAM_pop, echo=FALSE}
dat = ech_rep
name_dat = "GAM_ech_rep"


## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit=T)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)

y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3" )) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
ggsave(paste0("Sorties/pred_Y_GAM_","ech_rep","-vs-test.png"),width=7.29, height=4.5)


graph_Y = function (name_dat){
  ## target variable analysis
  print(ggplot() +
    geom_line(aes(x=test$X, y=y_pred, colour="pred"), lwd = 1.5) +
      geom_line(aes(x=test$X, y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
      geom_line(aes(x=test$X, y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
      geom_point(alpha=0.5,aes(x=test$X, y=y_test),colour="chartreuse4", shape=19, size=1)+
      stat_smooth(aes(x=test$X, y=y_test,colour="test"),method = loess, lwd=1.5)+
      scale_color_manual(name = "dataset",values = c("pred" = "deepskyblue4", "test" = "darkgreen", "conf_int" = "deepskyblue3")) +   
      theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")))
  ggsave(paste0("Sorties/pred_Y_",name_dat,"-vs-test.png"),width=7.29, height=4.5)
}
graph_Y(name_dat)

```

#### Imbalanced Sample

```{r predGAM_ech0, echo=FALSE}
dat = ech0
name_dat = "GAM_ech0"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### Weighted Resampling (WR) sample

```{r predGAM_ech_add, echo=FALSE}
dat = ech_add
name_dat = "GAM_ech_add"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### GN-WR sample

```{r predGAM_ech_GN_SC, echo=FALSE}
dat = ech_GN_SC
name_dat = "GAM_ech_GN_SC"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
```

#### GN_GMM-WR sample

```{r predGAM_GN_GMM, echo=FALSE}
dat = GN_GMM
name_dat = "GAM_GN_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### ROSE-WR sample

```{r predGAM_ech_ROSE_SC, echo=FALSE}
dat = ech_ROSE_SC
name_dat = "GAM_ech_ROSE_SC"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### ROSE_GMM-WR sample

```{r predGAM_ROSE_GMM, echo=FALSE}
dat = ROSE_GMM
name_dat = "GAM_ROSE_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### KDE-WR sample

```{r predGAM_kde_boot, echo=FALSE}
dat = kde_boot
name_dat = "GAM_kde_boot"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
```

#### KDE_GMM-WR sample

```{r predGAM_kde_boot_GMM, echo=FALSE}
dat = kde_boot_GMM
name_dat = "GAM_kde_boot_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### GMM-WR sample

```{r predGAM_GMM, echo=FALSE}
dat = GMM
name_dat = "GAM_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### FA_GMM-WR sample

```{r predGAM_FA_GMM, echo=FALSE}
dat = FA_GMM
name_dat = "GAM_FA_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### Copula-WR sample

```{r predGAM_ech_copule, echo=FALSE}
dat = ech_copule
name_dat = "GAM_ech_copule"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### GAN_GMM-WR sample

```{r predGAM_ech_ctganSynth_GMM, echo=FALSE}
dat = ech_ctganSynth_GMM
name_dat = "GAM_ech_ctganSynth_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
```

#### SMOTE-WR sample

```{r predGAM_ech_smote, echo=FALSE}
dat = ech_smote
name_dat = "GAM_ech_smote"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
```

#### SMOTE_GMM-WR sample

```{r predGAM_ech_smote_GMM, echo=FALSE}
dat = ech_smote_GMM
name_dat = "GAM_ech_smote_GMM"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

#### RF-WR sample

```{r predGAM_ech_RF2, echo=FALSE}
dat = ech_RF2
name_dat = "GAM_ech_RF2"

## Predictions
reg = gam(Y ~  s(X) , data = dat)
p <- predict(reg, test, se.fit = TRUE)
upr <- p$fit + (2 * p$se.fit)
lwr <- p$fit - (2 * p$se.fit)
y_pred = p$fit
res = summary(reg)
ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
gam_devExp[k] = res$dev.expl ; print(paste0("deviance expliquee : " , round(gam_devExp[k]*100,2)))
gam_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(gam_rmse[k]*100,2)))
gam_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(gam_R2[k]*100,2)))
gam_hell_X[k] = hellinger(pop$X, dat$X)
gam_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
gam_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
gam_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = 2) +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = 2) +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")) 
## ggsave(paste0("Sorties/pred_Y_GAM_","ech_RF","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)

```

## Random Forest Learning

```{r indic_RF,echo=F}
RF_rsq = rep(0,16)
RF_rmse = rep(0,16)
RF_R2 = rep(0,16)
RF_hell_X = rep(0,16)
RF_hell_Y = rep(0,16)
RF_kl_X = rep(0,16)
RF_kl_Y =rep(0,16)
k=1
```

#### Balanced sample

```{r predRF_pop, echo=FALSE}
dat = ech_rep
name_dat = "ech_rep"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)

p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
ggsave(paste0("Sorties/pred_Y_RF_","ech_rep","-vs-test.png"),width=7.29, height=4.5)


graph_Y_RF = function (name_dat){
  ## target variable analysis 
  print(ggplot() +
      stat_smooth(aes(x=test$X, y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
      stat_smooth(aes(x=test$X, y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
      stat_smooth(aes(x=test$X, y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
      geom_point(alpha=0.5,aes(x=test$X, y=y_test),colour="chartreuse4", shape=19, size=1)+
      stat_smooth(aes(x=test$X, y=y_test,colour="test"),method = loess, lwd=1.5)+
      scale_color_manual(name = "dataset",values = c("pred" = "deepskyblue4", "test" = "darkgreen", "conf_int" = "deepskyblue3")) +   
      theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold")))
 ggsave(paste0("Sorties/pred_Y_RF_",name_dat,"-vs-test.png"),width=7.29, height=4.5)
}
graph_Y_RF(name_dat)

```

#### Imbalanced sample

```{r predRF_ech0, echo=FALSE}
dat = ech0
name_dat = "ech0"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)

p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### Weighted Resampling (WR) sample

```{r predRF_ech_add, echo=FALSE}
dat = ech_add
name_dat = "ech_add"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)

p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)


```

#### GN-WR sample

```{r predRF_ech_GN_SC, echo=FALSE}
dat = ech_GN_SC
name_dat = "ech_GN_SC"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)

p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)


```

#### GN_GMM-WR sample

```{r predRF_GN_GMM, echo=FALSE}
dat = GN_GMM
name_dat = "GN_GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)


```

#### ROSE-WR sample

```{r predRF_ech_ROSE_SC, echo=FALSE}
dat = ech_ROSE_SC
name_dat = "ech_ROSE_SC"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### ROSE_GMM-WR sample

```{r predRF_ROSE_GMM, echo=FALSE}
dat = ROSE_GMM
name_dat = "ROSE_GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)


```

#### KDE-WR sample

```{r predRF_kde_boot, echo=FALSE}
dat = kde_boot
name_dat = "kde_boot"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)


```

#### KDE_GMM-WR sample

```{r predRF_kde_boot_GMM, echo=FALSE}
dat = kde_boot_GMM
name_dat = "kde_boot_GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### GMM-WR sample

```{r predRF_GMM, echo=FALSE}
dat = GMM
name_dat = "GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### FA_GMM-WR sample

```{r predRF_FA_GMM, echo=FALSE}
dat = FA_GMM
name_dat = "FA_GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### Copula-WR sample

```{r predRF_ech_copule, echo=FALSE}
dat = ech_copule
name_dat = "ech_copule"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### GAN_GMM-WR sample

```{r predRF_ech_ctganSynth_GMM, echo=FALSE}
dat = ech_ctganSynth_GMM
name_dat = "ech_ctganSynth_GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### SMOTE-WR sample

```{r predRF_ech_smote, echo=FALSE}
dat = ech_smote
name_dat = "ech_smote"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### SMOTE-GMM-WR sample

```{r predRF_ech_smote_GMM, echo=FALSE}
dat = ech_smote_GMM
name_dat = "ech_smote_GMM"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

#### RF-WR sample

```{r predRF_ech_RF2, echo=FALSE}
dat = ech_RF2
name_dat = "ech_RF2"

## Predictions
X = dat$X
pe = density(X,n=length(X))
pe = approx(pe$x,pe$y,xout=dat$X)$y
pt = Pt(X)
w = pt / pe
q = w / sum(w)
reg = randomForest( Y ~ X, data = dat, weights = q,nodesize=2)
p = predict(reg, test, predict.all=TRUE)
y_pred = p$aggregate
upr = apply(p$individual, 1, function(x) {quantile(x, 0.975)})
lwr = apply(p$individual, 1, function(x) {quantile(x, 0.025)})

ymax=max(y_pred,y_test)
ymin=min(y_pred,y_test)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
RF_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(RF_rsq[k]*100,2)))
RF_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(RF_rmse[k]*100,2)))
RF_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(RF_R2[k]*100,2)))
RF_hell_X[k] = hellinger(pop$X, dat$X)
RF_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
RF_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
RF_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), col="azure4") + stat_smooth(aes(y=y_test),method = loess, col="darkgreen", lwd=1.5)+
  ##geom_point(aes(y=y_pred), col="darksalmon", lwd=0.9) + 
  stat_smooth(aes(y=y_pred, colour="pred"), lwd=1.5, method='loess') + 
  stat_smooth(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  stat_smooth(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed", method='loess') +
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_RF_","ech0","-vs-test.png"),width=7.29, height=4.5)

graph_Y_RF(name_dat)

```

## Multivariate Adaptative Regression Spline Learning

```{r indic_MARS,echo=F}
mars_rsq = rep(0,16)
mars_rmse = rep(0,16)
mars_R2 = rep(0,16)
mars_hell_X = rep(0,16)
mars_hell_Y = rep(0,16)
mars_kl_X = rep(0,16)
mars_kl_Y = rep(0,16)
k=1
```

#### Balanced sample

```{r predMARS2_pop, echo=FALSE}
dat = ech_rep
name_dat = "MARS_ech_rep"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### Imbalanced sample

```{r predMARS2_ech0, echo=FALSE}
dat = ech0
name_dat = "MARS_ech0"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### Weighted Resampling (WR) sample

```{r predMARS2_ech_add, echo=FALSE}
dat = ech_add
name_dat = "MARS_ech_add"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
 
```

#### GN-WR sample

```{r predMARS2_ech_GN_SC, echo=FALSE}
dat = ech_GN_SC
name_dat = "MARS_ech_GN_SC"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### GN_GMM-WR sample

```{r predMARS2_GN_GMM, echo=FALSE}
dat = GN_GMM
name_dat = "MARS_GN_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### ROSE-WR sample

```{r predMARS2_ech_ROSE_SC, echo=FALSE}
dat = ech_ROSE_SC
name_dat = "MARS_ech_ROSE_SC"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### ROSE_GMM-WR sample

```{r predMARS2_ROSE_GMM, echo=FALSE}
dat = ROSE_GMM
name_dat = "MARS_ROSE_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### KDE-WR sample

```{r predMARS2_kde_boot, echo=FALSE}
dat = kde_boot
name_dat = "MARS_kde_boot"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
  
```

#### KDE_GMM-WR sample

```{r predMARS2_kde_boot_GMM, echo=FALSE}
dat = kde_boot_GMM
name_dat = "MARS_kde_boot_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### GMM-WR sample

```{r predMARS2_GMM, echo=FALSE}
dat = GMM
name_dat = "MARS_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### FA_GMM-WR sample

```{r predMARS2_FA_GMM, echo=FALSE}
dat = FA_GMM
name_dat = "MARS_FA_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### Copula-WR sample

```{r predMARS2_ech_copule, echo=FALSE}
dat = ech_copule
name_dat = "MARS_ech_copule"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### GAN_GMM-WR sample

```{r predMARS2_ech_ctganSynth_GMM, echo=FALSE}
dat = ech_ctganSynth_GMM
name_dat = "MARS_ech_ctganSynth_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1

## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### SMOTE-WR sample

```{r predMARS2_ech_smote, echo=FALSE}
dat = ech_smote
name_dat = "MARS_ech_smote"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### SMOTE_GMM-WR sample

```{r predMARS2_ech_smote_GMM, echo=FALSE}
dat = ech_smote_GMM
name_dat = "MARS_ech_smote_GMM"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
```

#### RF-WR sample

```{r predMARS2_ech_RF2, echo=FALSE}
dat = ech_RF2
name_dat = "MARS_ech_RF2"

## Predictions
reg = earth(dat$X ,dat$Y,nfold=10, ncross=30, varmod.method='gam')
p = predict(reg,test,interval="pint")
upr <- p$upr
lwr <- p$lwr
y_pred = p$fit
ymax=max(y_pred,ymax)
ymin=min(y_pred,ymin)
plot(y_test,y_pred)
abline(0,1,col='red')

## Indicators
mars_rsq[k] = mean(reg$rsq) ; print(paste0("pseudo-R2 : " , round(mars_rsq[k]*100,2)))
mars_rmse[k] = rmse(y_test,as.numeric(y_pred)) ; print(paste0("RMSE : " , round(mars_rmse[k]*100,2)))
mars_R2[k] = cor(y_test,as.numeric(y_pred))^2 ; print(paste0("R2 : " , round(mars_R2[k] *100,2)))
mars_hell_X[k] = hellinger(pop$X, dat$X)
mars_hell_Y[k] = hellinger(y_test, y_pred)
f_pop = densityfun(pop$X)
f_dat = densityfun(dat$X)
mars_kl_X[k] = kl.dist(f_pop(pop$X), f_dat(pop$X))$D
mars_kl_Y[k] = kl.dist(y_test,y_pred)$D
k = k + 1


## Graphics
plot(test$X,y_pred, xlab = "X (test)", ylab = "Yhat vs Y (test)", ylim=c(ymin,ymax))
points(test$X, y_test, col='red')

ggplot(data.frame(X=test$X,y_test,y_pred), aes(x=X)) + 
  geom_point(aes(y=y_test), colour="azure4") + stat_smooth(aes(y=y_test,colour="test"),method = loess, lwd=1.5)+
  geom_line(aes(y=y_pred, colour="pred"), lwd=1.5) + 
  geom_line(aes(y=upr, colour="conf_int"), lwd=1,linetype = "dashed") +
  geom_line(aes(y=lwr, colour="conf_int"), lwd=1,linetype = "dashed") +
  
  scale_color_manual(name = "y", values = c("test" = "chartreuse4", "pred" = "deepskyblue4","conf_int" = "deepskyblue3")) + theme(legend.position = c(.95, .95),legend.justification = c("right", "top"),legend.title = element_text(face = "bold"))
## ggsave(paste0("Sorties/pred_Y_MARS_","ech_rep","-vs-test.png"),width=7.29, height=4.5)

graph_Y(name_dat)
 
beepr::beep(8)
```
